\section{Experience} %{{{
%\cventry{year--year}{Job title}{Employer}{City}{}{Description}                % arguments 3 to 6 are optional%}}}
%%{{{--| MD @ LBJ
\cventry{05/2014 -- current}{Internal Medicine / Critical Care Physician /
Telemedicine Director}{LBJ TMC}{Pago-Pago}{American Samoa}{LBJ TMC is a rural community hospital of 150 bed capacity, with 7 ICU beds and 27 beds in  medical ward.
\newline -- Assessed and treated acute, chronic, and complex illnesses, in adolescents, adults, and elderly in accordance with the principles of evidence-based medical practice following USA guidelines. 
\newline -- Evaluated patients when different illnesses occur together or in situations where the diagnosis may be obscure. 
\newline -- Ordered laboratory, as well, as imaging tests, and subsequently interpreted results. 
\newline -- Prescribed and/or administered medication, therapy, and other specialized medical care to treat or prevent illness, disease, or injury. 
\newline -- Monitored patient's conditions and progress and re-evaluated treatments as necessary. 
\newline -- Collected, recorded, maintained and analyzed patient information, such as medical history, reports, and examination results on a daily basis. 
\newline -- Immunized patients to protect them from preventable diseases. 
\newline -- Explained and performed procedures and discussed test results or prescribed treatments to patients. 
\newline -- Participated in the island-wide colorectal screening program together with the surgical team, performed supervised upper and lower endoscopies. 
\newline -- Advised patients and community members concerning diet, activity, hygiene, and disease prevention. 
\newline -- Referred patient to medical specialist or other practitioner when necessary. 
\newline -- Provided in-flight medical escort during patient's transfer to other medical facilities 
\newline -- Provided consulting services to other doctors caring for patients with special or difficult problems in ER, ICU, Surgical ward, Dental, Dialysis clinics. 
\newline -- Advised surgeon of a patient's risk status and recommended appropriate intervention to minimize risk. 
\newline -- Directed and coordinated activities of nurses, assistants, specialists, therapists, and other medical staff. 
\newline -- Proctored physician assistants in training from Bryant University during their rotations. 
\newline -- Participated in COVID19 planning, preparation and vaccinations events. 
\newline -- Participated in the administrative meeting when required. 
\newline -- Lead and coordinated tele-medecine effort. 
\newline -- Moonlighted in emergency room. 
} %}}}

%%{{{--| Clinical Assistant @ Lipton Cardiology
\cventry{04/2013 -- 12/2013}{Clinical Assistant}{Dr.Lipton}{Brooklyn}{NY}{ -- Customized EHR and integrated practice from paper charts to digital records in compliance with CMS guidelines.
\newline -- Created new work-flow model to accommodate EHR implementation including balancing protocol for quality and safety measures.
\newline -- Maintained relations and troubleshoot all issues with EHR, laboratory, referring offices and pharmaceutical representatives.
\newline -- Interviewed patient to document history including immunization, preventative care, surgical history, active problems, nutritional and social history within EHR
\newline -- Performed clinical procedures including triage procedures, venipuncture, EKG and obtaining cultures.
\newline -- Administrative duties as required including authorizations, clinical review, insurance verification.}%}}}

%%{{{--| Observership in ER of Lutheran medical Center
\cventry{09 -- 10/2012}{Emergency Department Observer}{Lutheran Medical Center}{Brooklyn}{NY}{ -- Followed attending physicians and residents in ER. \newline -- Discussed clinical presentations, diagnostic and treatment plans.} % Reference Dr. Gloria Tsan - emergency medicine residency director %}}}

%%{{{--| RMA @ Urology4U
\cventry{05/2012 -- 04/2013}{Registered Medical Assistant}{Gene Meisenberg Medical Services, PC}{Brooklyn}{NY}{ -- Prepared patients and assisted physician with examinations, and during diagnostic and surgical procedures.
\newline -- Performed urodynamic / Videourodynamic studies utilizing C-Arm
\newline -- Performed uroflowmetry, biofeedback.
\newline -- Performed SC/IM injections and IV infusions
\newline -- Collected specimens and sent orders to ``Quality laboratory service'' or ``Quest diagnostics'' laboratories.
\newline -- Assessed patient's general condition and took vital signs.
\newline -- Promoted wellness by providing patient education materials, communicating physician advices, instructions. }%}}}

%%{{{--| Volunteer @ IANT Clinic
\cventry{01 -- 04/2012}{Internal Medicine Physician}{IANT clinic}{Richardson}{TX}{ -- Obtained HPI.
\newline -- Performed physical examinations.
\newline -- Identified relevant clinical findings.
\newline -- Developed differential diagnoses.
\newline -- Ordered lab tests and imaging studies.
\newline -- Formulated assessments and management plans.
\newline -- Prescribed medications [supervised].
\newline -- Adjusted treatment in chronic conditions according to current guidelines.}%}}}

%%{{{--| Volunteer @ Agape Clinic
\cventry{03/2011 -- 05/2012}{Internal Medicine Physician}{Agape clinic}{Dallas}{TX}{ -- Obtained HPI.
\newline -- Performed physical examinations.
\newline -- Identified relevant clinical findings.
\newline -- Developed differential diagnoses.
\newline -- Ordered in-house and outgoing lab tests as well as imaging studies.
\newline -- Formulated assessments and management plans.
\newline -- Prescribed medications [supervised].
\newline -- Adjusted treatment in chronic conditions according to current guidelines.}%}}}

%%{{{--| Externship @ The Heart Beat Clinic
\cventry{01/2011 -- 05/2012}{Extern}{The HeartBeat Clinic}{McKinney}{TX}{ -- Obtained HPI.
\newline -- Performed focused physical examinations [supervised]
\newline -- Identified relevant clinical findings.
\newline -- Developed differential diagnoses.
\newline -- Problem assessments.
\newline -- Formulated and discussed management plans with Dr.Suleman.}%}}}

%%{{{--| PSG @ SCOA
\cventry{05--11/2009}{Polysomnographic Technician}{Sleep Centers of America - now bankrupt }{Tarrant Co}{TX}{ --  Prepared testing equipment.
\newline -- Performed polysomnographic procedures (NPSG-DX, CPAP-TX, SPLIT-TX)}                % arguments 3 to 6 are optional%}}}

%%{{{--| RMA @ FAAP
\cventry{12/2013 -- 05/2014 \newline\newline 11/2008 -- 05/2012}{Registered Medical Assistant}{Frisco Allergy \& Asthma Center}{Frisco}{TX}{ -- Assessed patient's general condition and took vital signs.
\newline -- Prepared patients and assisted physician with examinations, diagnostic procedures and treatments.
\newline -- Performed PFT, Allergy Skin Tests, Neb treatments, RUSH procedures.
\newline -- Performed SC/IM injections, phlebotomy. Sent orders and specimens to ``LabCorp'' or ``Quest'' laboratories.
\newline -- Provided basic patient care and interventions in emergency situations.
\newline -- Documented all activities, interventions, patient or family responses, Rx'ed medication, etc., in EMR.
\newline -- Promoted wellness by providing patient education materials, communicating physician advices, instructions.
\newline -- Participated in EMR customization (eClinicalWorks).
\newline -- Answered telephones, greeted patients, scheduled appointments.}%}}}

%%{{{--| CRC @ ACRC  CRC @ ACRC Trials not for RMA position
\cventry{05 -- 10/2008}{Clinical Research Coordinator}{ACRC Trials}{Addison}{TX}{ -- Recruited patients for various clinical studies.
\newline -- Independently obtained informed consent for all types of clinical studies.
\newline -- Collected data and laboratory specimen.
\newline -- Assisted the Principal Investigator in the conduct of clinical studies.
\newline -- Prepared and submitted Case Report Forms (CRFs) or eCRFs and other data to the Sponsor.
\newline -- Prepared IRB/GCO submissions and regulatory filing including AE and SAE reports.
\newline -- Ensure sponsor and investigator obligations are being met and are in compliance with applicable ICH guidelines, Standard Operating Procedures (SOPs), local regulatory requirements, and internal policies.}
%\newline -- List of studies available upon request}
%\newline -- Conduct all aspects of the clinical trials, as requested to produce accurate and reliable data for the sponsor.
%\newline -- Designed and maintained organizational tools to conduct studies accurately and completely in compliance with GCP, FDA, study protocols, and internal policies.}%}}}

%%{{{--| RMA @ A-Care
\cventry{05/2005 -- 05/2008}{Registered Medical Assistant}{A-Care Medical P.A.}{Richardson}{TX}{ -- Gathered history of patient's present illness, concerns.
\newline -- Assessed patient's general condition and took vital signs.
\newline -- Prepared patients and assisted physician with examinations, diagnostic procedures and treatments.
\newline -- Performed ECG, ETT, Holter monitor, PFT, Tympanometry, ANS, VNG functional tests.
\newline -- Performed SC/IM injections, phlebotomy. Sent orders and specimens to ``LabCorp'' or ``Quest'' laboratories.
\newline -- Provided basic patient care as ordered.
\newline -- Documented all activities, interventions, patient or family responses, Rx'ed medication, etc., in EMR.
\newline -- Promoted wellness by providing patient education materials, communicating physician advices, instructions.
\newline -- Answered telephones, greeted patients, scheduled appointments.}%}}}

%%{{{--| RMA @ Denton County
\cventry{05/2004 -- 05/2005}{Health Services Specialist II}{Denton County Correctional Health}{Denton}{TX}{ -- Responded to emergency and non-emergency medical calls or requests in the County Jail and provided necessary medical attention.
\newline -- Assessed patient's general condition and performed procedures as ordered by physicians.
\newline -- Assisted in maintaining an adequate inventory of medical supplies.
\newline -- Created patient's chart and performed chart documentation duties which included logging all actions taken or orders received regarding the patient.}%}}}

%%{{{--| Volunteer @ Las Colinas Medical Center
\cventry{05/2003 -- 05/2004}{Emergency Department Observer}{Las Colinas Medical Center}{Irving}{TX}{ -- Followed attending physicians in ER. \newline -- Discussed clinical presentations, diagnostic and treatment plans.}%}}}

%%{{{--| Sysadmin @ Data Technologies
\cventry{12/2000 -- 05/2003}{Network system administrator}{Data Technologies}{Dallas}{TX}{ -- Installed, configured and troubleshooted various operation systems and software complexes.}%}}}

%%{{{--| MD @ IGMA
\cventry{09/1997 -- 11/2000}{Internal Medicine Physician}{Ivanovo State Medical Academy}{Ivanovo}{Russia}{ -- Diagnosed and provided non-surgical treatment of diseases and injuries of internal organ systems for adults.
\newline -- Examined patients with cardiovascular, pulmonary, gastrointestinal and genitourinary disturbances.
\newline -- Ordered diagnostic procedures.
\newline -- Prescribed treatment.
\newline -- Monitored therapy effects.
\newline -- Handled emergencies.
\newline -- Prescribed course of rehabilitation.
\newline -- Participated in high resolutions ECG research.
\newline -- Performed acupuncture.
} %}}}

%{{{-| Miscellaneous blank |
%\subsection{Miscellaneous}
%\cventry{year--year}{Job title}{Employer}{City}{}{Description line 1\newline{}Description line 2}% arguments 3 to 6 are optional
%}}}
%{{{--| Experience example |
%\section{Experience}
%\subsection{Vocational}
%\cventry{year--year}{Job title}{Employer}{City}{}{General description no longer than 1--2 lines.\newline{}%
%Detailed achievements:%
%\begin{itemize}%
%\item Achievement 1;
%\item Achievement 2, with sub-achievements:
%  \begin{itemize}%
%  \item Sub-achievement (a);
%  \item Sub-achievement (b), with sub-sub-achievements (don't do this!);
%    \begin{itemize}
%    \item Sub-sub-achievement i;
%    \item Sub-sub-achievement ii;
%    \item Sub-sub-achievement iii;
%    \end{itemize}
%  \item Sub-achievement (c);
%  \end{itemize}
%\item Achievement 3.
%\end{itemize}}
%\cventry{year--year}{Job title}{Employer}{City}{}{Description line 1\newline{}Description line 2}
%\subsection{Miscellaneous}
%\cventry{year--year}{Job title}{Employer}{City}{}{Description} %}}}
%\section{Extra 1} %{{{
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem[+]{Item 3}            % optional other symbol
%\renewcommand{\listitemsymbol}{-} % change the symbol for lists
%\section{Extra 2}
%\cvlistdoubleitem{Item 1}{Item 4}
%\cvlistdoubleitem{Item 2}{Item 5 \cite{book1}}
%\cvlistdoubleitem{Item 3}{}
%}}}
